Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
conclusion

%===============================================================================
\section{Concluding Remarks}
%===============================================================================
\rmcmt{
In this paper, we presented a novel HW/SW co-verification tool, \verifox,
for C-based FW and hardware models given in Verilog RTL.  We presented a
notion of transaction in joint RTL and FW models.  We showed that the
interaction pattern between FW and HW transactions can be exploited to
generate a unified co-verification model.  To this end, we presented a
path-based symbolic execution technique to automatically infer
scenario/transaction pairs from a co-verification model.  Our general observation
is that monolithic BMC based approaches cannot exploit these interactions
and thus generate very complex formulas, which are difficult to solve. 
Owing to specific optimizations in \verifox such as eager path pruning
combined with incremental SAT solving, we experimentally show that \verifox
is an order of magnitude faster than the state-of-the-art HW/SW
co-verification tool, \hwcbmcv.  We demonstrate applicability of our
approach for proving safety as well as finding FW-HW bugs for a UART IP and
a SoC design.  In the future, we plan to extend our framework to FW-HW
models that exhibit further interaction patterns.
}
%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{abbrv}
\bibliography{biblio}

>>>>

%===============================================================================
\section{Concluding Remarks}
%===============================================================================
%
In this paper, we presented two approaches for verification of 
HW/SW co-designs using formal techniques.  These approaches are 
embodied in our tool \hwcbmcv and \verifox.  We presented a 
notion of scenario and transaction for effective verification 
of co-designs.  To this end, we presented a path-based algorithm
to automatically mine scenario/transaction pairs.  We showed that 
the construction of a co-verification model must leverage specification of 
co-design properties over hardware and firmware events in order to 
successfully apply formal methods in co-verification.  To enable this, we 
presented two types of co-design properties, \emph{transaction level} and 
\emph{component level}.  Our tools support co-designs written in Verilog RTL 
and C.

Our general observation is that monolithic BMC based approaches 
cannot prune irrelevant transactions with respect to a given scenario, 
and hence generate very complex formulas, which are difficult to solve. 
Owing to specific optimizations in \verifox such as eager path pruning
combined with incremental SAT solving, we experimentally show that \verifox
is an order of magnitude faster than the \hwcbmcv.  We demonstrate applicability of our
approach for proving safety as well as finding critical co-design bugs for 
a UART IP and a complex SoC design.  In the future, we plan to extend our 
framework to co-design models that exhibit further interaction patterns.

%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{abbrv}
\bibliography{biblio}
